FictionEro - Affective Impact of Fiction

### 2025-09-02 analysis/analysis.qmd
updated script

@@

tbl_results <-   function(model1, title_table = "Fixed Effects: Study 1"){

  # ---- Fixed effects table ----
  tbl <- parameters::parameters(model1, effects = "fixed") |>
    as.data.frame() |>
    select(-Effects, -df_error, -CI) |>
    gt() |>
    # tab_header(title = title_table, subtitle = subtitle_table) |>
    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
    cols_label(
      Parameter = "Predictor",
      Coefficient = "β",
      SE = "SE",
      CI_low = "CI (lower)",
      CI_high = "CI (upper)",
      z = "z-value",
      p = "p"
    ) |>
    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
    cols_label(`CI_low` = "95% CI") |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) |>
    opt_table_lines()

    return(tbl)
}

  plt <- pred_df |>
    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
    )) +
    geom_hline(yintercept = 0, color = "darkgrey") +
    geom_line(size = 1) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
    facet_grid(Relevance ~ Gender, switch = "y") +
    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
    theme_minimal(base_size = 14) +
    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
    ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 8),
      strip.placement = "outside",
      strip.background.x = element_rect(fill = "lightgrey", color = NA),
      strip.text.x = element_text(size = 10),
      strip.text.y = element_text(size = 10),
      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
      legend.text = element_text(size = 10),
      legend.position = "bottom"
    )

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")

tbl_a1 <- tbl_results(arousal1, title = "Fixed Effects: Arousal Study 1")
tbl_a1
```

```{r}
tbl_a2 <- tbl_results(arousal2, title = "Fixed Effects: Arousal Study 2")
tbl_a2
```

```{r}
plta <- make_combined_plot(arousal1, arousal2, title = "Arousal Estimates for All Stimuli")
```

@@

```{r}
enticement1 <- readRDS("models/ModelEnticement_1.rds")
enticement2 <- readRDS("models/ModelEnticement_2.rds")

tbl_e1 <- tbl_results(enticement1, title = "Fixed Effects: Enticement Study 1")
tbl_e1
```

```{r}
tbl_e2 <- tbl_results(enticement2, title = "Fixed Effects: Enticement Study 2")
tbl_e2
```

```{r}
plt_e <- make_combined_plot(enticement1, enticement2, title = "Enticement Estimates for All Stimuli")
plt_e
```

@@

```{r}
valence1 <- readRDS("models/ModelValence_1.rds")
valence2 <- readRDS("models/ModelValence_2.rds")

tbl_v1 <- tbl_results(valence1, title = "Fixed Effects: Valence Study 1")
tbl_v1
```

```{r}
tbl_v2 <- tbl_results(valence2, title = "Fixed Effects: Valence Study 2")
tbl_v2
```

```{r}
plt_v <- make_combined_plot(valence1, valence2, title = "Valence Estimates for All Stimuli")
plt_v
```

@@

>>>>

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

@@

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

```{r}
results_table(arousal1)
```

```{r}
results_table(arousal2)

```{r}
#| fig-height: 8
#| fig-width: 8

  plt <- pred_df |>
    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
    )) +
    geom_hline(yintercept = 0, color = "darkgrey") +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
    facet_grid(Relevance ~ Gender, switch = "y") +
    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
    theme_minimal(base_size = 14) +
    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
    ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 8),
      strip.placement = "outside",
      strip.background.x = element_rect(fill = "lightgrey", color = NA),
      strip.text.x = element_text(size = 10),
      strip.text.y = element_text(size = 10),
      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
      legend.text = element_text(size = 10),
      legend.position = "bottom")

plta <- make_combined_plot(arousal1, arousal2, title = "Arousal Estimates for All Stimuli")

plta
```

@@

```{r}
enticement1 <- readRDS("models/ModelEnticement_1.rds")
enticement2 <- readRDS("models/ModelEnticement_2.rds")
```

```{r}
results_table(enticement1)
```

```{r}
results_table(enticement2)
```

```{r}
#| fig-height: 8
#| fig-width: 8

plt_e <- make_combined_plot(enticement1, enticement2, title = "Enticement Estimates for All Stimuli")
plt_e
```

@@

```{r}
valence1 <- readRDS("models/ModelValence_1.rds")
valence2 <- readRDS("models/ModelValence_2.rds")
```

```{r}
results_table(valence1)
```

```{r}
results_table(valence2)
```

```{r}
#| fig-height: 8
#| fig-width: 8

plt_v <- make_combined_plot(valence1, valence2, title = "Valence Estimates for All Stimuli")
plt_v
```

@@

table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = "green", domain = c(0, 1)) |> 
    gt::fmt_auto()
}

g1 <- modelbased::estimate_grouplevel(arousal1)
table_dvour(g1)

```{r}
g2 <- modelbased::estimate_grouplevel(arousal2)
table_dvour(g2)
```
